Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-23 manuscript/draft.Rmd
fig 4 clarify

![None of the models provided a consistent improvement over the "average"
baseline, indicated by a horizontal line. **A.** Models' absolute error was
generally similar or larger than "average" model, with large outliers in both
directions. **B.** The other models' deviance was also generally higher than the
"average" baseline.](../figures/model_violins.png)

>>>>

![Site/year difference between the average model and all other models in absolute
error (**A.**) and deviance (**B.**). All testing years (2004-2013) are used here. 
None of the five other models provided a consistent improvement over the "average"
baseline, indicated by a horizontal line. Models' absolute error was generally
similar or larger than "average" model, with large outliers in both directions.
The other models' deviance was also generally higher than the "average"
baseline.](../figures/model_violins.png)
